\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}
\title{\textbf{"Rent4Vent"}}
\author{Devesh Kumar, 19112014}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

\setlength{\parskip}{1em}

\large Rent4Vent is basically an online platform (an app) where the needy meet the provider. In simple words, there are many people who migrate to different cities in because of jobs, pursuing their study, expand their businesses, etc. with or without families. They are often in search of flats, pgs, etc. as they cannot afford the hotel rooms for more than a certain period of time with required features. Eventually there are so many rental flats and pg rooms which are available for rent. So, how can a person find its perfect stay? 

\setlength{\parskip}{1em}


\large{\textbf{There are mainly two ways:  }}
\begin{itemize}
    \item 	Roaming in a big city which is completely new to them and search for their stay: This creates too much hassle as they do not have any idea about the city and environment of that particular area. For example if that area is suitable for studies and has required necessities nearby. The another obvious option is,
    \item	To hire a broker and take his/her help: First of all finding a broker is one of a challenge itself. And even if you find one, they also have a region which they know about and beyond that region they are clueless. They also charge 50 percent of the commission on an average from the customer and the owner both which is obviously too much money, just to guide the customer.
    
\setlength{\parskip}{1em}

\large So our company comes up with a third option by arranging a space where the customers can find their destination. 
    
\end{itemize}

\section{Marketing}

Target audience: This venture covers a vast range of audience, this includes people staying away from their homes such as students, workers, labourers, etc. And it also covers everyone who have any vacant areas, flats, rooms, etc. to rent.

\setlength{\parskip}{1em}

\large{\textbf{Types of Marketing are: }}
\begin{itemize}
    \item {\textbf{Service Marketing}} - Service marketing is the marketing and selling of intangible products (non-physical products). Services comprise all of those personal facilities which we require from time to time like; medical care, education, renting of living spaces and vehicles, hair cut, spas, musical concerts, dance classes, etc.
    \item {\textbf{e - Marketing}} - E-marketing is an advertising discipline that includes all marketing activities conducted by a business online using an electronic device or the internet. Other names for this type of marketing include internet marketing, online marketing, digital marketing or web marketing.
    \item {\textbf{Social Marketing}} - Social marketing is an approach used to develop activities aimed at changing or maintaining people's behaviour for the benefit of individuals and society as a whole. For example, it might encourage people to reduce their consumption of fast food or alcohol, increase their consumption of organic food, and encourage a healthy lifestyle in the health sector.
    \item {\textbf{Holistic Marketing}} - Holistic marketing considers a business and all its parts. It sees a business as one entirety. For example where does a business fit into the broader economy. And how does it impact the lives of its customers. Think of the human body that can only function when all parts are working together.
    \item {\textbf{Green Marketing}} - Green marketing refers to the practice of developing and advertising products based on their real or perceived environmental sustainability. When a company's green marketing activities are not substantiated by significant investments or operational changes, they may be criticized for false or misleading advertising.
\end{itemize}





\end{document}