\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}
\title{\textbf{Sales and Marketing for "Sadabahar"}}
\author{Chelsy Gangwar, 19112012}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

\setlength{\parskip}{1em}

\large In this Venture we’ll look at the Marketing strategies which will be used of “Sadabahar”. So, it seems very exciting to work on such topic which is related to our daily life. As we’re all aware of why it is so much important for us and what are the benefits of planting trees and plants. 
\setlength{\parskip}{1em}

\large Coming to the Marketing Strategies which we’ll require to take our venture at a reputed position will be discussed in this paper and what all things that are required for marketing of this particular team/venture.

\setlength{\parskip}{1em}

\large What is Marketing?

\large It refers to different types of activities that a company/team needs to do to promote their selling or buying of a service or product. Marketing includes selling of goods, advertising the product and delivering it to the customers.

\setlength{\parskip}{1em}

\section{Types of Marketing are: }
\begin{itemize}
    \item {\textbf{Service Marketing}} - The marketing and sale of intangible things is referred to as service marketing (non-physical products). Medical treatment, teaching, rental of living places and automobiles, beauty treatments, spas, musical concerts, dance courses, and other personal services are all included in the category of services.
    \item {\textbf{E - Marketing}} - E-marketing is a marketing practise that encompasses all marketing efforts carried out by a company using an electronic gadget or the internet. Internet marketing, online marketing, digital marketing, and web marketing are all terms used to describe this sort of marketing.
    \item {\textbf{Social Marketing}} - Social marketing is a strategy for altering or sustaining people's behaviour for the well-being of people as well as society overall. It may, for example, empower individuals to consume less junk food and alcohol and consume more organic food, as well as improve health and well-being in the health sector.
    \item {\textbf{Holistic Marketing}} - Holistic marketing takes into account all aspects of a business. It considers a company as a whole. For instance, how does a company integrate into the larger economy? What impact does it have on the lifestyles of its customers? Consider the human body, which can only operate when all of its components are in sync.
    \item {\textbf{Green Marketing}} - Green marketing is the process of creating and marketing goods that are dependent on its actual or perceived environmental protection. When a company's green marketing efforts aren't backed up by major investments or modifications, they risk being accused of dishonest or fraudulent advertising.
\end{itemize}

\setlength{\parskip}{1em}

\section{Plants Market Scope and Market Size}

\large The market for indoor plants in India is estimated at over Rs 250 crores annually and is growing at 15. 

\setlength{\parskip}{1em}

Rising air pollution concerns in not only the metros but in smaller towns across the country has made indoor plant a much-needed solution for people, leading them to add more green inside their homes. Also, this has led to increased awareness of indoor plants.

\setlength{\parskip}{1em}

The indoor plants market is segmented on the basis of type, application and product.

\begin{itemize}
    \item On the basis of types, the indoor plants market is segmented into shade- loving plants, low light plants and high light plants.
    \item On the basis of product, the indoor plants market is segmented into succulent plants, berbaceous plants, woody plants and hydroponic plants.
    \item On the basis of application, the indoor plants market is segmented into absorb harmful gases and home decoration.
\end{itemize}

\section{Business Model}

\large Currently we are still figuring out, though we are looking for:
\begin{itemize}
    \item Aggregator Business Model: 
    
    Aggregator Business Model is a network model where the aggregator firm collects information about particular offering providers, sign contracts with such providers, and sell their services under its own brand.
    
    Since the aggregator is a brand, it provides an offering that has uniform quality and price, even though it is offered by different partner providers. 
    
    The offering providers never become aggregator’s employees and continue to be the owners of the product or service provided. Aggregator just helps them in marketing in a unique win-win manner. 
   
    
    For us it will mean that we will be having a platform which will have products listed by us by partnering with a single or only a bunch of supplier, basically selling the plants under our brand name.
    
    We can try this model for our plant based venture but for now its chances seems less.
    
    \item Marketplace business model:
    
    A marketplace is a platform where buyers and sellers interact and trade through a network.
    
    The online marketplace doesn’t own any products or services. It simply acts as a mediator and connects buyers and sellers.
    
    In other words, a marketplace is a platform that provides value to both buyers and sellers. Sellers get a place to sell their products and grow their brand while buyers are provided with multiple choices and high-quality products all in one place.
    
    For us it will mean that we will be having a platform which will have multiple plant sellers and buyers choosing from the listed products.
    
    We are more interested in this model, though we are figuring out how can we become an essential part of our partners business and develop a unique selling point.
    
    \item Personal Brand
    
    Like doing everything on our own, growing plants on our own, maintaining them on our own.
    
    This is the least possible thing.

\end{itemize}

\section{Actual Ground situation}

\large I along with my team visited more than 5 nurseries this week, and came to know that 4 of them didn’t grew indoor plants on their own and just bought them from places like Pune, Kolkata and Andhra Pradesh. Only 1 nursery owner claimed to grow the plants in Raipur itself though we are not sure how sure her claim is.

So now we are figuring out how to procure plants for our venture. For now we are sure that we will be able to find even one nursery that grow the plant by itself in Raipur and partner with it.

\section{Customer Insights}

\large We have conducted customer survey of 39 people, where the results were

   100\% users were of 18-40 age group. 
   
   66.7\% of users preferred a plant priced below Rs500 and 66.7\% of users buyied it from local nurseries.
   
   66.7\% buyied indoor plants for Decorative purposes. 
   
   30.8\% buyied to reduce harmful gases, while 48.7\% buyied indoor plants because they liked to do so without any special reason.
   
   38.5\% of the user felt that the problem must be solved. 56.4\% of the people felt that the problem may be solved. 5.1\% said that the problem isn’t valuable to them.
   


\section{B2B Marketing Strategies:}
\begin{itemize}
    \item Content Marketing
    \item Inbound Marketing
    \item Social Media Marketing
    \item Search Engine Marketing
    \item Account Based Marketing(ABM) and Re-targeting
    \item Conversational Marketing
    \item Industry Events
\end{itemize}

\section{B2C Marketing Strategies:}
\begin{itemize}
    \item Social Network and Viral Marketing
    \item Internet Marketing
    \item Email Marketing
    \item Direct Selling
    \item Point of Purchase (POP) Marketing
    \item Paid Media Advertising
\end{itemize}

 
\section{About Venture}

Your venture is focused on providing counselling for selecting plants, suggestions for correct place to keep plants, plants, raw materials, real time assistance, easy accessibility, and IOT features for plant care. 


\section{Conclusion}

With growing evidence to support the notion that plants can play an important role in providing a higher quality living environment, people are getting increasing interested in buying them. The market size of indoor plants is also growing, so, and with start of entry of big players, this is the best time to enter the market. But we will have to keep in mind that this industry comes with its own risk.



\end{document}