\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}
\title{\textbf{"Rent4Vent"}}
\author{Devesh Kumar, 19112014}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

\setlength{\parskip}{1em}

\large Rent4Vent is basically an online platform (an app) where the needy meet the provider. In simple words, there are many people who migrate to different cities in because of jobs, pursuing their study, expand their businesses, etc. with or without families. They are often in search of flats, pgs, etc. as they cannot afford the hotel rooms for more than a certain period of time with required features. Eventually there are so many rental flats and pg rooms which are available for rent. So, how can a person find its perfect stay? 

\setlength{\parskip}{1em}




\large{\textbf{There are mainly two ways:  }}
\begin{itemize}
    \item 	Roaming in a big city which is completely new to them and search for their stay: This creates too much hassle as they do not have any idea about the city and environment of that particular area. For example if that area is suitable for studies and has required necessities nearby. The another obvious option is,
    \item	To hire a broker and take his/her help: First of all finding a broker is one of a challenge itself. And even if you find one, they also have a region which they know about and beyond that region they are clueless. They also charge 50 percent of the commission on an average from the customer and the owner both which is obviously too much money, just to guide the customer.
    
\setlength{\parskip}{1em}

\large So our company comes up with a third option by arranging a space where the customers can find their destination. 
    
\end{itemize}






\end{document}